Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-24 draft.tex
expand results section

			The black-box model described in the previous section was trained on the first //TODO//
			samples in the dataset. Evaluation was then performed on the remaining samples in the

@@

@@

>>>>

			The black-box model described in the previous section was trained on the first portion
			of the dataset, differing depending on the exact experiment (more details are provided
			in the next section). Evaluation was then performed on the remaining samples in the

@@

	Using the methods described in the previous section, I performed experiments training and
	testing the surrogate model, as well as generating many explanations for the purpose of
	aggregate evaluation. This section will first discuss the results and performance of the
	surrogate model, followed by an evaluation of the aggregated explanations.

@@

		A summary of some experiments based on the method described above is provided below. The
		model that achieved the best results was trained and evaluated using the methods
		previously described, has an evaluation accuracy of 96.3\% with the default threshold of
		0.5. EER is approximately 0.03214. This outperforms other results tested in the original
		paper on this dataset \cite{muller_does_2022}. This result also exceeds some other results
		tested on this dataset \cite{yang_robust_2024}, produced using a variety of imperceptible
		features and trained on the ASV2019 dataset, while underperforming one other method
		\cite{ranjan_statnet_2022} that made use of raw waveform-based features, training on 70
		percent of the data in the dataset, validating on 10 percent and testing on the remaining
		20 percent.
